### 2013-04-19 inst/examples/BUGS/allen.Rmd
parametric bayes intial example

```{r}
mcmc <- as.mcmc(jagsfit)
mcmcall <- mcmc[,-2]
mcmcall <- cbind(mcmcall[,1],mcmcall[,2],mcmcall[,3],mcmcall[,4],mcmcall[,5])
## get parameter estimates (and transform inverse variances back to SDs)
coef <- apply(mcmcall,2,mean)
coef[2:3]=log(sqrt(1/coef[2:3]));
coef[4:5]=exp(coef[2:3]);

coef.median<-apply(mcmcall,2,median)
coef.median[2:3]=log(sqrt(1/coef.median[2:3]));
coef.median[4:5]=exp(coef.median[4:5]);

dens<-apply(mcmcall,2,density)
coef.mode<-sapply(dens,function(x) x$x[which.max(x$y)] )
coef.mode[2:3]=log(sqrt(1/coef.mode[2:3]));
coef.mode[4:5]=exp(coef.mode[4:5]);

ci.mc <- t(apply(mcmcall,2,quantile, probs=c(0.025,0.975)))
## OBS remember that upper and lower are reversed!
ci.mc[2:3,2:1]=log(sqrt(1/ci.mc[2:3,]));
ci.mc[4:5,]=exp(ci.mc[4:5,]);

##reorder the stuff (K,Q,R,r0,theta)=>(theta r0 K Q R)
myorder=c(5,4,1,2,3);
coef=coef[myorder];
coef.median=coef.median[myorder];
coef.mode=coef.mode[myorder];
ci.mc=ci.mc[myorder,];

convinfo=list(effsize=effectiveSize(mcmc), geweke=geweke.diag(mcmc))       ## MCMC convergence info

>>>>

```{r}
mcmc <- as.mcmc(jagsfit)
mcmcall <- mcmc[,-2]
who <- colnames(mcmcall)
mcmcall <- cbind(mcmcall[,1],mcmcall[,2],mcmcall[,3],mcmcall[,4],mcmcall[,5])
colnames(mcmcall) <- who
```

```{r}
theta <- exp(mcmcall[,"logtheta"])
theta_dist <- hist(theta, freq=FALSE)
theta_dist$mids
theta_dist$density
delta <- theta_dist$mids[2] - theta_dist$mids[1]
```

evaluating the value function given $f$ fixed at each of `theta_dist$mids` multiplied by  `theta_dist$density * delta` and summed over each $\theta$ is going to be slow for a single parameter but simply unrealistic for higher dimensions.  Instead we will rely on Monte Carlo sampling of parameter values from their posteriors,

```{r}
mc_n <- 100
thetas <- sample(theta, mc_n, replace=T)
